Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-20 cav2017/cav2017.tex
todos+typo

\subsubsection{Computing the set of reachable states}
\todo{explain the use of abstract acceleration}

@@

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to 
compute a candidate solution $K$. It does this by assuming 
a $k$ and a sampling rate. The check that this assumptions were sound 
will be performed later by the {\sc complete} and {\sc sampling} 
validation stages.

>>>>

\todo{Move as much as possible from Sec~\ref{sec:cof_verification}
to the appendix (e.g. discussion on abstract acceleration). 
Merge the rest in Sec~\ref{sec:cof_synth}.}

@@

1. The inductive synthesis phase (i.e. {\sc synthesize}) uses BMC to 
compute a candidate solution $K$. It does this by assuming 
a $k$ and a sampling rate. The check that this assumptions were sound 
is performed later by the {\sc complete} and {\sc sampling} 
validation stages.
